---
output: rmarkdown::github_document
---

`rgeocodio` : Tools to Work with the <https://geocod.io/> 'API'

NOTE: You need an [API key](https://dash.geocod.io/) to use this package.

The following functions are implemented:

- `gio_auth`:	Get or set GEOCODIO_API_KEY value
- `gio_batch_geocode`:	Geocode up to 10,000 addresses
- `gio_batch_reverse`:	Reverse geocode up to 10,000 coordinates
- `gio_geocode`:	Geocode a single address
- `gio_geocode_components`:	Geocode a single address
- `gio_reverse`:	Reverse geocode a single lat/lon pair

### TODO

- enable selection of additional fields
- better return types
- more error checking
- tests

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/rgeocodio")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(rgeocodio)

# current verison
packageVersion("rgeocodio")

gio_geocode("1109 N Highland St, Arlington, VA")

gio_geocode_components("1109 N Highland St", "Arlington", "VA")

gio_reverse(38.9002898, -76.9990361)

gio_batch_geocode(c(
  "1109 N Highland St, Arlington VA",
  "525 University Ave, Toronto, ON, Canada",
  "4410 S Highway 17 92, Casselberry FL",
  "15000 NE 24th Street, Redmond WA",
  "17015 Walnut Grove Drive, Morgan Hill CA"
))

data.frame(
  lat = c(35.9746000, 32.8793700, 33.8337100, 35.4171240),
  lon = c(-77.9658000, -96.6303900, -117.8362320, -80.6784760)
) -> to_code

gio_batch_reverse(to_code)
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(rgeocodio)
library(testthat)

date()

test_dir("tests/")
```

